---
title: "Raju Rishikesh Gollapally Business Analytics Assignment-1 "
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
  pdf_document: default
Date: "09-30-2023"
---

#Install the ISLR library operating the install.packages() command.
    #install.packages("ISLR")
    #As this ISLR package is already installed it will not reveal any error that the package is already installed.
    

#Calling the ISLR library using the library(ISLR) command to ensure that the library is correctly installed.

```{r}
library(ISLR)

```

#Considering the data set file Carseats that is present in the ISLR Library.

```{r}
View(Carseats)

```

#Printing the summary of the Carseats dataset

```{r}
summary(Carseats)

```

#Printing the  maximum value of the advertising attribute that is present in Carseats datset.

```{r}
max(Carseats$Advertising)

```
#Printing the  maximum value of the Price attribute that is present in Carseats datset.

```{r}
max(Carseats$Price)

```

#Summing up the Inter Quartile Range(Upper Range-Lower range) of the Price attribute

```{r}
IQR(Carseats$Price)

```

#Summing up the correlation between Sales VS Price
#Conspiring the Sales against Price

```{r}
plot(Carseats$Sales,Carseats$Price,main = "Ploting the sales againest Price", xlab="sales", ylab = "Price")

```
#In This graph plot shows both the attributes Sales and Price in the y-axis and x-axis respectively. We can also see the pattern of the plots as to how the design is slant downwards.



# Calculating the correlation of the two attributes(sales vS Price).

```{r}
cor.test(Carseats$Sales, Carseats$Price, method = c("pearson"))

```
#The result we obtained from the code is -0.4449507. The negative symbol indicates that the correlation coeffecient is weakly neagtive. The plot graph design also shows the same pattern.
